Optimizing and Incrementalizing Collection Queries by AST Transformations

### 2017-07-21 chap-intro.tex
Remove/revise references to part:caching

This thesis is divided into three parts:
\begin{itemize}
\item In \cref{part:ch-aosd13}, we describe work on optimizing collection
  queries by static program transformation, based on a set of rewrite rules~\citep{GiarrussoAOSD13}.
\item In \cref{part:incr}, we describe work on incrementalizing programs
  by static program transformation. This thesis presents the first approach that
  handles higher-order programs by using program transformation; hence, while
  our main examples use collection queries, we phrase the work in terms of
  $\lambda$-calculi with unspecified primitives~\citep*{CaiEtAl2014ILC}.
\item In \cref{part:caching}, we extend ILC with a further program transformation
  step, so that base programs can store intermediate results and derivatives can
  reuse them, but without resorting to dynamic memoization and necessarily
  needing to look results up at runtime. To this end, we build on work by
\citet{Liu00} and extend it to a higher-order, typed setting.
\end{itemize}

\Cref{part:incr} and \cref{part:caching} are more theoretical than
\cref{part:ch-aosd13}. That was necessary, because optimizations in
\cref{part:ch-aosd13} are much better understood than our approach to
incrementalization.

@@

\pg{Describe \cref{part:caching}}
\pg{Paste contributions from paper}
\pg{Maybe defunc chapter?}

@@

% Write this even though maybe I restructure the parts.
\Cref{part:incr} and \Cref{part:caching} describe incrementalization.

>>>>

This thesis is divided into three parts:
\begin{itemize}
\item In \cref{part:ch-aosd13}, we describe work on optimizing collection
  queries by static program transformation, based on a set of rewrite rules~\citep{GiarrussoAOSD13}.
\item In \cref{part:incr}, we describe work on incrementalizing programs
  by static program transformation. This thesis presents the first approach that
  handles higher-order programs by using program transformation; hence, while
  our main examples use collection queries, we phrase the work in terms of
  $\lambda$-calculi with unspecified primitives~\citep*{CaiEtAl2014ILC}.
  In \cref{ch:cts}, we extend ILC with a further program transformation
  step, so that base programs can store intermediate results and derivatives can
  reuse them, but without resorting to dynamic memoization and necessarily
  needing to look results up at runtime. To this end, we build on work by
\citet{Liu00} and extend it to a higher-order, typed setting.
\end{itemize}

\Cref{part:incr} is more theoretical than
\cref{part:ch-aosd13}. That was necessary, because optimizations in
\cref{part:ch-aosd13} are much better understood than our approach to
incrementalization.

@@

\pg{Describe \cref{ch:cts}}
\pg{Paste contributions from paper}
\pg{Maybe defunc chapter?}

@@

% Write this even though maybe I restructure the parts.
\Cref{part:incr} describes incrementalization.
